### 2023-02-07 definitions.tex
Up

remarque si on enlève la strong monotony mais en gardant with effective basis of $post^*$:

\begin{proposition}(à prouver)
 leur algorithme for {\sc bounded resilience} termine mais pas correct for WSTS with upward compatibility, not necessarly strong, and an effective basis of $post^*$ ?
\end{proposition}

>>>>

remarque si on enlève la strong monotony mais en gardant with effective basis of $\uparrow post^*$:

\begin{proposition}(à prouver)
 leur algorithme for {\sc bounded resilience} termine mais pas correct for WSTS with upward compatibility, not necessarly strong, and an effective basis of $\uparrow post^*$ ?
\end{proposition}
